My Linux Notes

### 2018-08-12 Ubuntu_16.04_setup/mylinux.Rmd
up

---
title: "My Linux Notes"
subtitle: "A Quick Reference"
author: "[Yongfu Liao](https://liao961120.github.io/)"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
link-citations: yes
output:
  bookdown::html_document2:
    highlight: haddock
    css: /home/liao/local_depend/style_sheets/style.css
    df_print: kable
    toc: true
    toc_depth: 2
    toc_float:
        collapsed: false
---

@@

>>>>

---
title: "My Linux Notes"
subtitle: "A Quick Reference"
author: "[Yongfu Liao](https://liao961120.github.io/)"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
link-citations: yes
output:
  bookdown::html_document2:
    css: /home/liao/local_depend/style_sheets/style.css
    df_print: kable
    toc: true
    toc_depth: 2
    toc_float:
        collapsed: false
---

@@

RegEx
========

**MetaCharacters**

- `.`: Any character.

- `+`: **1 or more**, e.g. `s+aa` matches 1 or more `s` followed by `aa`.

- `*`: **0 or more**, e.g. `s*aa` matches 0 or more `s` followed by `aa`.

- `{#}`: **Exact #**, e.g. `s{2}` matches strings with exactly 2 `s`(equivalent to `ss`).
	- `{#_1, #_2}`: **Between #_1 & #_2**.

- `(<some.char>)`: Use `(` & `)` to **group**
	- `(na){2}`: matches ba**nana**.
